### 2016-11-27 Hhh/Hhh.tex
Removing table option
Full detector chapter and first part of H->hh corrections

\chapter{\texorpdfstring{Search for \Htohhtobbtautau}{Search for H -> hh -> bbtautau}}
\label{sec:hhh}
In this chapter the search for a heavy Higgs boson decaying to a pair of 125 GeV Higgs bosons, with one of these Higgs bosons decaying to 
a pair of b-jets and the other decaying to a pair of \Ptau leptons is discussed. In this analysis the \etau, \mutau and \tautau final states
of the \Pgt-pair are studied, these final states are referred to as channels.
The results of this search are model-independent
upper limits on heavy Higgs production cross--section times branching ratio into h(125)h(125)$\rightarrow b\bar{b} \tau\tau$, for
which all three channels are combined. The \etau and \mutau channels will be described in this chapter, the \tautau channel will not
be covered, although the limits shown in section \ref{sec:hhh_results} will include this final state.
In addition  the results are interpreted in the context of the MSSM and a type-II Two Higgs Doublet Model (2HDM), 
these interpretations are made in combination with the results of a search for \AtoZhtolltautau. 
This search will be summarised in this chapter, but will not constitute the main focus.
Both searches, and their interpretation, are detailed in reference \cite{CMS-HIG-14-034}.

The discovery of the 125 GeV Higgs boson by the ATLAS and CMS collaborations in 2012 \cite{HDiscoveryAtlas,HDiscoveryCMS} has opened up
new possibilities for probing the Higgs sector beyond the Standard Model. As discussed in chapter THEORY, in some MSSM scenarios, and some more
generic type-II 2HDM's, a heavy neutral Higgs boson H can decay to a pair of 125 GeV Higgs bosons for low values
of \tanb, probing a region of phase space not yet excluded by stringent existing limits. In regions where
the decay \Htohh is enhanced, the \AtoZh decay also has a large branching ratio, indicating the usefulness
of both channels for probing the low-\tanb region. The $b\bar{b}$\tautau final state is chosen for the combination
of the large $h(125) \rightarrow b\bar{b}$ branching ratio and the cleaner \htotautau final state.

\section{Datasets and \acl{MC} samples}
\label{sec:hhh_datasets}
The dataset used for this analysis corresponds to the full dataset collected by the CMS experiment during the 2012 $p-p$ 
running period of the LHC. 
Signal and background events were generated using several different \ac{MC} event generators. The \texttt{MadGraph}
\cite{madgraph} matrix element generator was used to generate samples of \Wjets, \Zellell, \ttbar and \ZZ ,\WZ and \WW
events. In addition to samples with a mixture of jet multiplicities (`inclusive' samples), samples binned in jet multiplicity
were used for the \Wjets and \Zellell backgrounds. This increases the background event statistics
in regions with multiple jets, which important for this analysis due to the presence of b-jets in the searched-for final state. 
The samples binned in jet multiplicity are combined with the
inclusive samples such that the fraction of events with each jet multiplicity is preserved.

Single top samples were produced with the \texttt{POWHEG} \cite{powheg1,powheg2} generator. Samples of $gg\rightarrow$\Htohhtobbtautau
were generated in steps of 10 GeV between \mH $= 260 - 350$~GeV using \texttt{PYTHIA 6} \cite{pythia64}. In all of the samples
\texttt{TAUOLA} \cite{tauola} is used to decay $\tau$s, and parton showering and hadronisation are modelled using \texttt{PYTHIA 6} \cite{pythia64}.
Minimum bias events generated using \texttt{PYTHIA 6} are added to all \ac{MC} samples to model additional
interactions.

To better model the \Ztautau background, an embedding technique is used. In this method, 
\Zmm events are selected in data and the muons are replaced by generator-level taus. \texttt{TAUOLA} is used
to decay the taus and tau polarisation effectes are modelled using \texttt{TauSpinner} \cite{TauSpinner}. The detector
response to the tau decay products is modelled using the \texttt{GEANT4}-based \cite{Geant4} detector simulation, and 
tracks in the inner tracking system, hits in the muon systems and energy deposits in the calorimeters
due to the simulated taus are combined with the remains of the \Zmm event after the detector signals
of the two muons originiating from the \PZ have been removed. This technique is also applied to 
a \ttbar background sample to estimate the \ttbar contamination in the embedded sample. This contribution
needs to be subtracted from the \Ztautau background estimated using the embedded \Zmm sample to
avoid double counting with the \ttbar \ac{MC}.

\section{Event selection and categorisation}
\label{sec:hhh_selection}
A more detailed description of the physics objects used for this analysis is given in chapter OBJECTS
in this section only an overview of the event selection is presented.

\subsection{\texorpdfstring{Event selection in the \mutau channel}{Event selection in the mu-tau channel}}
\label{sec:hhh_selection_mutau}
The first step of event selection in the \mutau channel is a trigger 
which requires only a muon
at L1. At the level of the HLT a hadronic tau, reconstructed using a simpler version of the
PF algorithm, is also required. Loose isolation requirements are applied to this hadronic tau, and 
loose ID and isolation requirements are applied to the muon at this stage.

In the offline event selection, an oppositely charged \mutau pair is required, 
separated by $\Delta R > 0.5$.
The muon is required to have a \pT~of at 
least 20 GeV and $|\eta| < 2.1$, and should be compatible with originating from the 
primary vertex. This means the impact parameters $d_{xy}$ and $d_{z}$ must be smaller
than 0.045 and 0.2 cm respectively. Tight muon identification
criteria and tight isolation requirements $I_{\text{rel}}^{\mu} < 0.1$, as described 
in section OBJECTS, are applied. The hadronic tau must have a \pT~of at least
20 GeV, $|\eta| < 2.3$, and must have $d_{z} < 0.2$ cm. It is required to pass 
the decay mode finding identification
from the HPS algorithm, as described in section OBJECTS. Additionally
the raw combined isolation, described in the same section, is required to be
at most 1.5 GeV. To reject $\Pe/\Pgm \rightarrow \Pgt_{h}$ fakes, and to
reduce the contribution of \Zmm background events, the hadronic tau is 
also required to pass the tight working point of the anti-$\Pgm$ discriminator
and the loose working point of the cut--based anti-$\Pe$ discriminator, both
described in section OBJECTS.

@@

After the trigger selection, an oppositely charged \etau pair is required, again separated by $\Delta R >0.5$. 
The electron should have a \pT~of at least 24 GeV, $|\eta| < 2.1$, and should
satisfy $d_{xy} < 0.045$cm and $d_{z} < 0.2$ cm. The electron must pass the tight
working point of the electron MVA ID discriminator described in section OBJECTS, and the
relative isolation is required to be $I_{rel}^{\Pe} < 0.1$. The requirements placed on the
hadronic tau are similar to those required in the \mutau channel, apart from the anti-$\Pgm$ discriminator,
where the loose working point is required, and the anti--$\Pe$ discriminator, where the medium
working point of the MVA discriminator is required.

If there is more than one possible \etau pair, the pair with largest \pT$^{\Pe}$+\pT$^{\Pgt_{h}}$
is taken. Similar additional vetos as in the \mutau channel are applied.
the event is rejected if an opposite--charge pair of electrons with \pT $> 15$ GeV, passing looser ID and
isolation requirements than the signal electron requirements can be formed. To reduce the \WZ
background, events that have more than one electron or at least one muon passing \pT $>10$ GeV and loose ID and isolation
requirements are rejected.

@@

\subsection{Categorisation}
\label{sec:hhh_selection_categories}
In both channels a selection on the transverse mass \mT~between the electron/muon
and missing transverse energy, defined as in equation \ref{eqn:hhh_selection_mt}, is applied.
\begin{equation}\label{eqn:hhh_selection_mt}
m_{\text{T}} = \sqrt{2p_{\text{T}}E_{\text{T}}^{\text{miss}}(1-\cos{\Delta\phi})}
\end{equation}
In this eqation \pT~is the transverse momentum of the electron or muon, and $\Delta\phi$ the angle
between the light lepton and the missing transverse energy. The \mT~distributions for the \etau
and \mutau channels, using the selections as
described in sections \ref{sec:hhh_selection_mutau} and \ref{sec:hhh_selection_etau},
are shown in figure \ref{fig:Hhh_selection_mt}.

@@

After applying the \mT~selection, events are divided into three categories to maximise
sensitivity to the signal: 2jet-0tag (at least 2 jets, exactly 0 of which are b-tagged), 2jet-1tag 
(at least 2 jets, exactly 1 of which is b-tagged), 2jet-2tag (at least 2 jets, at least 2 of which are b-tagged).
Jets are considered b-tagged if they pass the medium working point of the b-tagging discriminator described in section OBJECTS.
The 2jet-0tag category does not collect much of the signal and is dominated by 
backgrounds, the 2jet-2tag category is most sensitive to signal. 
Figure \ref{fig:Hhh_selection_bjets}, which shows the number of b-tagged jets in the 2-jet selection of the \mutau and \etau
channels, illustrates this.

@@

In signal events, the di--tau pair and di--jet pair 
are the decay products of an 125 Gev Higgs boson, therefore their invariant
masses should be close to 125 GeV. To reduce background contributions
from events where the di--tau or di--jet mass is not compatible with
125 GeV, requirements are made on the di--jet invariant mass and the di--tau
invariant mass as reconstructed using the \texttt{SVFit} algorithm \cite{HDiscoveryCMS,SVFit}. This algorithm provides
a likelihood-based estimate of the di-tau mass using the visible decay products
of the taus and the reconstructed \MET. The use of this algorithm greatly
improves the separation between $Z\rightarrow\Pgt\Pgt$ and $H\rightarrow\Pgt\Pgt$ events, 
which is of great importance for the SM $H\rightarrow\Pgt\Pgt$ analysis \cite{HDiscoveryCMS}.
By requiring $70 < m_{jj} < 150 $GeV and $90 < m_{\Pgt\Pgt} < 150$ GeV a 
large number of background events can be rejected, while retaining
most of the signal. This is illustrated in figure \ref{fig:Hhh_selection_masscuts} for 
the 2jet-2tag category.

@@

To correct for the difference in b--tagging efficiency and light jet mis--tagging
rates between data and \ac{MC} \pT~and $\eta$~dependent scale factors are 
derived using the method described in \cite{BTV8TeV}. There are separate scale factors for 
b-/c- jets and light jets. Multiple possible ways to apply these scale factors
exist, for this analysis this is done through a promote/demote method.

In this method a demotion or promotion probability is assigned to every
jet as in equation \ref{eqn:promotedemote}.
\begin{align}\label{eqn:promotedemote}
&P(\text{demote}) = 1 - SF \text{  for SF < 1 }  \notag \\
&P(\text{promote}) = \frac{(SF - 1)(\epsilon_{\text{MC}}-1)}{SF} \text{    for SF > 1}
\end{align}
In this equation $SF$ is the scale factor mentioned above, and $\epsilon_{\text{MC}}$ is
the b--tagging efficiency in \ac{MC} events for the type of jet (light, b- or c-)
in consideration.

\section{Discriminating variable}
\label{sec:hhh_discr}
The variable of interest in this analysis is the mass of the heavy Higgs boson H. This can be
reconstructed as the 4--body mass of the two jets and the two taus, however
a more accurate result can be obtained by using a kinematic fitting 
procedure that makes use of the 125 GeV mass constraint on the di--tau and
di--jet candidates.

@@

Before the fit, from the mass constraint we have (equation \ref{eqn:kinfit_prefit})
~\vspace{-0.5\baselineskip}
\begin{align}\label{eqn:kinfit_prefit}
m_{h}^2 &= E_{h}^2 - \vec{p_{h}}^2 = (E_{b1}+E_{b2})^2 - (\vec{p_{b1}} + \vec{p_{b2}})^2 \notag\\
& = 2E_{b1}E_{b2} + m_{b1}^2 +m_{b2}^2 - 2\vec{p_{b1}}\vec{p_{b2}} \notag\\
& = m_{b1}^2 +m_{b2}^2 - 2E_{b1}E_{b2}(1-\vec{\beta_{b1}}\vec{\beta_{b2}})\notag\\
&\Rightarrow (1-\vec{\beta_{b1}}\vec{\beta_{b2}}) = \frac{m_h^2 - m_{b1}^2 - m_{b2}^2}{2E_{b1}E_{b2}}
\end{align}
When varying the energy of the first jet in the fit, equation \ref{eqn:kinfit_prefit} can be 
rewritten to derive an expression for the updated energy of the second jet. Using $\mathcal{A} = (1-\vec{\beta_{b1}}\vec{\beta_{b2}})$ 
and equation \ref{eqn:gamma_def}:
~\vspace{-0.5\baselineskip}
\begin{equation}\label{eqn:gamma_def}
\gamma = \frac{1}{1-\beta^2} \Rightarrow \gamma^2 = \frac{1}{1-\beta^2} = \frac{1}{1-p^2/E^2} = \frac{E^2}{m^2}
\end{equation}
We get:
~\vspace{-0.5\baselineskip}
\begin{align}\label{eqn:kinfit_variation}
m_h^2 &= m_{b1}^2 + m_{b2}^2 - 2E_{b1}E_{b2}(1-\vec{\beta_{b1}}\vec{\beta{b2}})\notag\\
&= m_{b1}^2 +\frac{E_{b2,fit}^2}{\gamma_{b2}^2} +2\mathcal{A}E_{b1}E_{b2,fit}\notag\\
\Rightarrow E_{b2}^{fit}& = \frac{(-2E_{b1}\mathcal{A} + \sqrt{4E_{b1}^2\mathcal{A} - 4(m_{b1}^2-m_{h}^2)\gamma_{b2}^{-2}})\gamma_{b2}^2}{2}\notag\\
&= - E_{b1}\mathcal{A}\gamma_{b2}^2+\sqrt{E_{b1}^2\mathcal{A}\gamma_{b2}^4 - (m_{b1}^2 - m_{h}^2)\gamma_{b2}^2}\notag\\
&\Rightarrow E_{b2}^{fit} = E_{b1}\mathcal{A}\gamma_{b2}^2(-1 + \sqrt{1+\frac{m_{h}^2 - m_{b1}^2}{E_{b1}^2\mathcal{A}\gamma_{b2}^2}})
\end{align}

The fitting procedure additionally modifies the masses of the b-jets as (equation \ref{eqn:kinfit_bjetmass})
~\vspace{-0.5\baselineskip}
\begin{equation}\label{eqn:kinfit_bjetmass}
m_{b_{1,2}}^{fit} = m_{b_{1,2}}\frac{E_{b_{1,2}}^{fit}}{E_{b_{1,2}}}
\end{equation}
The $\chi^2$ term for each b-jet is calculated as $\chi_{b1,2}^2 = \frac{E_{b1,2}^{fit}-E_{b1,2}^{meas}}{\sigma_{b1,2}}$.

@@

The measured recoil is (equation \ref{eqn:kinfit_recoilmeas})
~\vspace{-0.5\baselineskip}
\begin{equation}\label{eqn:kinfit_recoilmeas}
\vec{p_{\text{T,recoil}}}^{\text{meas}} = -\vec{p_{\text{T,H}}}^{\text{meas}} = -\vec{p_{\text{T,miss}}}^{\text{meas}} - \vec{p_{\text{T},b_{1}}}^{\text{meas}} - \vec{p_{\text{T},b_{2}}}^{\text{meas}} - \vec{p_{\text{T},\Pgt_1^{\text{vis}}}}^{\text{meas}} - \vec{p_{\text{T},\Pgt_2^{\text{vis}}}}^{\text{meas}}
\end{equation}
With the recoil from the fit (equation \ref{eqn:kinfit_recoilfit})
~\vspace{-0.5\baselineskip}
\begin{equation}\label{eqn:kinfit_recoilfit}
\vec{p_{\text{T,recoil}}}^{fit} = -\vec{p_{\text{T,H}}}^{fit} = - \vec{p_{\text{T},b_{1}}}^{fit} - \vec{p_{\text{T},b_{2}}}^{fit} - \vec{p_{\text{T},\Pgt_1}}^{fit} - \vec{p_{\text{T},\Pgt_2}}^{fit}
\end{equation}
A $\chi^2$ corresponding to the agreement between the fitted and measured recoil is reconstructed as (equation \ref{eqn:kinfit_recoilchi2})
~\vspace{-0.5\baselineskip}
\begin{equation}\label{eqn:kinfit_recoilchi2}
\chi^2_{\text{recoil}} = (\vec{p_{\text{T,recoil}}}^{\text{fit}} - \vec{p_{\text{T,recoil}}}^{\text{measured}})^T V_{\text{recoil}}^{-1}(\vec{p_{\text{T,recoil}}}^{\text{fit}} - \vec{p_{\text{T,recoil}}}^{\text{measured}})
\end{equation}
where the covariance matrix $V_{\text{recoil}}$ of the recoil vector is estimated as in equation \ref{eqn:kinfit_recoilcov} from the covariance matrices of the b-jets and
the covariance matrix of the missing transverse momentum. The latter is estimated in the process of determining the MVA \MET as discussed in the
OBJECTS section,
while the covariance matrices of the b-jets can be written in terms of position, momentum and resolution of the b-jets. 
~\vspace{-0.5\baselineskip}
\begin{equation}\label{eqn:kinfit_recoilcov}
V_{\text{recoil}} = V_{\vec{p_{\text{T,miss}}}} - V_{b_{1}} - V_{b_2} 
\end{equation}
The total $\chi^2$ term that needs to be minimised in the fit can then be written as (equation \ref{eqn:kinfit_chitot})
~\vspace{-0.5\baselineskip}
\begin{equation}\label{eqn:kinfit_chitot}
\chi^2 = \chi^2_{b_1} + \chi^2_{b_2} + \chi^2_{\text{recoil}}
\end{equation}
The result of the kinematic fit are the tau and b-jet 4-vectors with their energies and momenta
set to the best fit values found for them in the fit. These can then be added together to find
the mass of the heavy Higgs boson as reconstructed by the kinematic fit.

>>>>

\chapter{\texorpdfstring{Search for \Htohhtobbtautau}{Search for H -> hh -> bbtautau}}
\label{sec:hhh}
In this chapter the search for a heavy Higgs boson decaying to a pair of 125 GeV Higgs bosons, with one of these Higgs bosons decaying to 
a pair of b-jets and the other decaying to a pair of \Ptau leptons is discussed. In this analysis, which 
uses a dataset corresponding to 19.8 fb$^{-1}$ collected during the 2012 p--p running
period of the \ac{LHC}, the \etau, \mutau and \tautau final states
of the \Pgt-pair are studied; these final states are referred to as channels. 
The results of this search are model-independent
upper limits on the heavy Higgs production cross--section times branching ratio into h(125)h(125)$\rightarrow b\bar{b} \tau\tau$, for
which all three channels are combined. The \etau and \mutau channels will be described in this chapter, the \tautau channel will not
be covered, although the limits shown in section \ref{sec:hhh_results} will include this final state.
In addition  the results are interpreted in the context of the MSSM and a type-II Two Higgs Doublet Model (2HDM), 
these interpretations are made in combination with the results of a search for \AtoZhtolltautau \cite{CMS-HIG-14-034}. 
My work focussed on checks for the \mutau and \etau channels, as well as being
responsible for limit setting for the \Htohh analysis, and performing the model interpretations
of the \Htohh and \AtoZh analyses, plus their combination.
Both searches, and their interpretation, are detailed in reference \cite{CMS-HIG-14-034}.

The discovery of the 125 GeV Higgs boson by the ATLAS and CMS collaborations in 2012 \cite{HDiscoveryAtlas,HDiscoveryCMS} has opened up
new possibilities for probing the Higgs sector beyond the Standard Model. As discussed in chapter THEORY, in some MSSM scenarios, and some more
generic type-II 2HDM's, a heavy neutral Higgs boson H can decay to a pair of 125 GeV Higgs bosons for low values
of \tanb, probing a region of phase space not yet excluded by the stringent existing limits. In regions where
the decay \Htohh is enhanced, the \AtoZh decay also has a large branching ratio, indicating the usefulness
of both channels for probing the low-\tanb region. The $b\bar{b}$\tautau final state is chosen for the combination
of the large $h(125) \rightarrow b\bar{b}$ branching ratio and the cleaner \htotautau final state.

\section{Datasets and \acl{MC} samples}
\label{sec:hhh_datasets}
The dataset used for this analysis corresponds to the full dataset collected by the CMS experiment during the 2012 $p-p$ 
running period of the LHC. 
Signal and background events were generated using several different \ac{MC} event generators. The \texttt{MadGraph}
\cite{madgraph} matrix element generator was used to generate samples of \Wjets, \Zellell, \ttbar and \ZZ ,\WZ and \WW
events. In addition to samples with a mixture of jet multiplicities (`inclusive' samples), samples binned in jet multiplicity
were used for the \Wjets and \Zellell backgrounds. This increases the number of background events
in regions with multiple jets, which are important for this analysis due to the presence of b-jets in the final state. 
The samples binned in jet multiplicity are combined with the
inclusive samples such that the fraction of events with each jet multiplicity is preserved.

Single top samples were produced with the \texttt{POWHEG} \cite{powheg1,powheg2} generator. Samples of $gg\rightarrow$\Htohhtobbtautau
were generated in steps of 10 GeV between \mH $= 260 - 350$~GeV using \texttt{PYTHIA 6} \cite{pythia64}. The signal
\ac{MC} is limited to 350 GeV because for the interpretation of a resonance as a Higgs boson the decay \PHiggs $\rightarrow$ \ttbar
starts to dominate beyond this mass. In all of the samples
\texttt{TAUOLA} \cite{tauola} is used to decay $\tau$s, and parton showering and hadronisation are modelled using \texttt{PYTHIA 6} \cite{pythia64}.
Minimum bias events generated using \texttt{PYTHIA 6} are added to all \ac{MC} samples to model additional
interactions.

To better model the \Ztautau background, an embedding technique is used. In this method, 
\Zmm events are selected in data and the muons are replaced by generator-level taus. \texttt{TAUOLA} is used
to decay the taus and tau polarisation effects are modelled using \texttt{TauSpinner} \cite{TauSpinner}. The detector
response to the tau decay products is modelled using the \texttt{GEANT4}-based \cite{Geant4} detector simulation, and 
tracks in the inner tracking system, hits in the muon systems and energy deposits in the calorimeters
due to the simulated taus are combined with the remains of the \Zmm event after the detector signals
of the two muons originiating from the \PZ have been removed. This technique is also applied to 
a \ttbar background sample to estimate the \ttbar contamination in the embedded sample. This contribution
needs to be subtracted from the \Ztautau background estimated using the embedded \Zmm sample to
avoid double counting with the \ttbar \ac{MC}.

\section{Event selection and categorisation}
\label{sec:hhh_selection}
This section gives an overview of the event selection, a detailed description of the physics
objecs used in this analysis is given in chapter OBJECTS.

\subsection{\texorpdfstring{Event selection in the \mutau channel}{Event selection in the mu-tau channel}}
\label{sec:hhh_selection_mutau}
The first step of event selection in the \mutau channel is a trigger 
which requires only a muon
at \ac{L1}. At the level of the \ac{HLT} a hadronic tau, reconstructed using a simpler version of the
\ac{PF} algorithm, is also required. Loose isolation requirements are applied to this hadronic tau, and 
loose ID and isolation requirements are applied to the muon at this stage.

In the offline event selection, an oppositely charged \mutau pair is required, 
separated by $\Delta R > 0.5$.
The muon is required to have a \pT~of at 
least 20 GeV and $|\eta| < 2.1$, and should be compatible with originating from the 
primary vertex. This means the impact parameters $d_{xy}$ and $d_{z}$ must be smaller
than 0.045 and 0.2 cm respectively. Tight muon identification
criteria and tight isolation requirements $I_{\text{rel}}^{\mu} < 0.1$, as described 
in section OBJECTS, are applied. The hadronic tau must have a \pT~of at least
20 GeV, $|\eta| < 2.3$, and must have $d_{z} < 0.2$ cm. It is required to pass 
the decay mode finding identification
from the HPS algorithm. Additionally
the raw combined isolation is required to be
at most 1.5 GeV. To reject $\Pe/\Pgm \rightarrow \Pgt_{h}$ fakes, and to
reduce the contribution of \Zmm background events, the hadronic tau is 
also required to pass the tight working point of the anti-$\Pgm$ discriminator
and the loose working point of the cut--based anti-$\Pe$ discriminator.

@@

After the trigger selection, an oppositely charged \etau pair is required, again separated by $\Delta R >0.5$. 
The electron should have a \pT~of at least 24 GeV, $|\eta| < 2.1$, and should
satisfy $d_{xy} < 0.045$cm and $d_{z} < 0.2$ cm. The electron must pass the tight
working point of the electron MVA ID discriminator, and the
relative isolation is required to be $I_{rel}^{\Pe} < 0.1$. The requirements placed on the
hadronic tau are similar to those required in the \mutau channel, apart from the anti-$\Pgm$ discriminator,
where the loose working point is required, and the anti--$\Pe$ discriminator, where the medium
working point of the MVA discriminator is required.

If there is more than one possible \etau pair, The pair with largest \pT$^{\Pe}$+\pT$^{\Pgt_{h}}$
is taken. Similar additional vetos as in the \mutau channel are applied.
the event is rejected if an opposite--charge pair of electrons with \pT $> 15$ GeV, passing looser ID and
isolation requirements than the signal electron requirements, can be formed. To reduce the \WZ
background, events that have more than one electron or at least one muon passing \pT $>10$ GeV and loose ID and isolation
requirements are rejected.

@@

\subsection{Categorisation}
\label{sec:hhh_selection_categories}
In both channels a selection on the transverse mass, \mT,~between the electron/muon
and missing transverse energy, defined as in equation \ref{eqn:hhh_selection_mt}, is applied.
\begin{equation}\label{eqn:hhh_selection_mt}
m_{\text{T}} = \sqrt{2p_{\text{T}}E_{\text{T}}^{\text{miss}}(1-\cos{\Delta\phi})}
\end{equation}
In this eqation \pT~is the transverse momentum of the electron or muon, and $\Delta\phi$ the azimuthal
angle between the light lepton and the missing transverse energy. The \mT~distributions for the \etau
and \mutau channels, using the selections as
described in sections \ref{sec:hhh_selection_mutau} and \ref{sec:hhh_selection_etau},
are shown in figure \ref{fig:Hhh_selection_mt}.

@@

After applying the \mT~selection, events are divided into three categories to maximise
sensitivity to the signal: 2jet-0tag (at least 2 jets, exactly 0 of which are b-tagged), 2jet-1tag 
(at least 2 jets, exactly 1 of which is b-tagged), 2jet-2tag (at least 2 jets, at least 2 of which are b-tagged).
Jets are considered b-tagged if they pass the medium working point of the \ac{CSV} b-tagging discriminator.
The 2jet-0tag category does not collect much of the signal and is dominated by 
backgrounds, the 2jet-2tag category is the most sensitive to signal. 
Figure \ref{fig:Hhh_selection_bjets}, which shows the number of b-tagged jets in the 2-jet selection of the \mutau and \etau
channels, illustrates this.

@@

In signal events, the di--tau pair and di--jet pair 
are the decay products of a 125 GeV Higgs boson, therefore their invariant
masses should be close to 125 GeV. To reduce background contributions
from events where the di--tau or di--jet mass is not compatible with
125 GeV, requirements are made on the di--jet invariant mass and the di--tau
invariant mass as reconstructed using the \texttt{SVFit} algorithm \cite{HDiscoveryCMS,SVFit}. This algorithm provides
a likelihood-based estimate of the di-tau mass using the visible decay products
of the taus and the reconstructed \MET. The use of this algorithm greatly
improves the separation between $Z\rightarrow\Pgt\Pgt$ and $H\rightarrow\Pgt\Pgt$ events, 
which is of great importance for the SM $H\rightarrow\Pgt\Pgt$ analysis \cite{HDiscoveryCMS}.
By requiring $70 < m_{jj} < 150 $GeV and $90 < m_{\Pgt\Pgt} < 150$ GeV a 
large number of background events can be rejected, while retaining
most of the signal. This is illustrated in figure \ref{fig:Hhh_selection_masscuts} for 
the 2jet-2tag category.

@@

To correct for the difference in b--tagging efficiency and light jet mis--tagging
rates between data and \ac{MC} \pT~and $\eta$~dependent scale factors are 
derived using the method described in ref. \cite{BTV8TeV}. There are separate scale factors for 
b-/c- jets and light jets. Multiple possible ways to apply these scale factors
exist, for this analysis this is done through a promote/demote method.

In this method a demotion or promotion probability is assigned to every
jet as in equation \ref{eqn:promotedemote}.
\begin{align}\label{eqn:promotedemote}
&P(\text{demote}) = 1 - SF \text{  for SF < 1 }  \notag \\
&P(\text{promote}) = \frac{(SF - 1)(\epsilon_{\text{MC}}-1)}{SF} \text{    for SF > 1}
\end{align}
In this equation $SF$ is the scale factor mentioned above, and $\epsilon_{\text{MC}}$ is
the b--tagging efficiency in \ac{MC} events for the type of jet (light, b- or c-)
under consideration.

\section{Discriminating variable}
\label{sec:hhh_discr}
The variable of interest in this analysis is the mass of the heavy Higgs boson H. This can be
reconstructed as the 4--body mass of the two jets and the two taus; however
a more accurate result can be obtained by using a kinematic fitting 
procedure that makes use of the 125 GeV mass constraint on the di--tau and
di--jet candidates.

@@

Before the fit, from the mass constraint we have:
~\vspace{-0.5\baselineskip}
\begin{align}\label{eqn:kinfit_prefit}
m_{h}^2 &= E_{h}^2 - \vec{p_{h}}^2 = (E_{b1}+E_{b2})^2 - (\vec{p_{b1}} + \vec{p_{b2}})^2 \notag\\
& = 2E_{b1}E_{b2} + m_{b1}^2 +m_{b2}^2 - 2\vec{p_{b1}}\vec{p_{b2}} \notag\\
& = m_{b1}^2 +m_{b2}^2 - 2E_{b1}E_{b2}(1-\vec{\beta_{b1}}\vec{\beta_{b2}})\notag\\
&\Rightarrow (1-\vec{\beta_{b1}}\vec{\beta_{b2}}) = \frac{m_h^2 - m_{b1}^2 - m_{b2}^2}{2E_{b1}E_{b2}}.
\end{align}
When varying the energy of the first jet in the fit, equation \ref{eqn:kinfit_prefit} can be 
rewritten to derive an expression for the updated energy of the second jet. Using $\mathcal{A} = (1-\vec{\beta_{b1}}\vec{\beta_{b2}})$ 
and
~\vspace{-0.5\baselineskip}
\begin{equation}\label{eqn:gamma_def}
\gamma = \frac{1}{1-\beta^2} \Rightarrow \gamma^2 = \frac{1}{1-\beta^2} = \frac{1}{1-p^2/E^2} = \frac{E^2}{m^2}.
\end{equation}
We get:
~\vspace{-0.5\baselineskip}
\begin{align}\label{eqn:kinfit_variation}
m_h^2 &= m_{b1}^2 + m_{b2}^2 - 2E_{b1}E_{b2}(1-\vec{\beta_{b1}}\vec{\beta{b2}})\notag\\
&= m_{b1}^2 +\frac{E_{b2,fit}^2}{\gamma_{b2}^2} +2\mathcal{A}E_{b1}E_{b2,fit}\notag\\
\Rightarrow E_{b2}^{fit}& = \frac{(-2E_{b1}\mathcal{A} + \sqrt{4E_{b1}^2\mathcal{A} - 4(m_{b1}^2-m_{h}^2)\gamma_{b2}^{-2}})\gamma_{b2}^2}{2}\notag\\
&= - E_{b1}\mathcal{A}\gamma_{b2}^2+\sqrt{E_{b1}^2\mathcal{A}\gamma_{b2}^4 - (m_{b1}^2 - m_{h}^2)\gamma_{b2}^2}\notag\\
&\Rightarrow E_{b2}^{fit} = E_{b1}\mathcal{A}\gamma_{b2}^2(-1 + \sqrt{1+\frac{m_{h}^2 - m_{b1}^2}{E_{b1}^2\mathcal{A}\gamma_{b2}^2}})
\end{align}

The fitting procedure additionally modifies the masses of the b-jets as 
~\vspace{-0.5\baselineskip}
\begin{equation}\label{eqn:kinfit_bjetmass}
m_{b_{1,2}}^{fit} = m_{b_{1,2}}\frac{E_{b_{1,2}}^{fit}}{E_{b_{1,2}}}.
\end{equation}
The $\chi^2$ term for each b-jet is calculated as $\chi_{b1,2}^2 = \frac{E_{b1,2}^{fit}-E_{b1,2}^{meas}}{\sigma_{b1,2}}$.

@@

The measured recoil is 
~\vspace{-0.5\baselineskip}
\begin{equation}\label{eqn:kinfit_recoilmeas}
\vec{p_{\text{T,recoil}}}^{\text{meas}} = -\vec{p_{\text{T,H}}}^{\text{meas}} = -\vec{p_{\text{T,miss}}}^{\text{meas}} - \vec{p_{\text{T},b_{1}}}^{\text{meas}} - \vec{p_{\text{T},b_{2}}}^{\text{meas}} - \vec{p_{\text{T},\Pgt_1^{\text{vis}}}}^{\text{meas}} - \vec{p_{\text{T},\Pgt_2^{\text{vis}}}}^{\text{meas}},
\end{equation}
and the recoil from the fit is,
~\vspace{-0.5\baselineskip}
\begin{equation}\label{eqn:kinfit_recoilfit}
\vec{p_{\text{T,recoil}}}^{fit} = -\vec{p_{\text{T,H}}}^{fit} = - \vec{p_{\text{T},b_{1}}}^{fit} - \vec{p_{\text{T},b_{2}}}^{fit} - \vec{p_{\text{T},\Pgt_1}}^{fit} - \vec{p_{\text{T},\Pgt_2}}^{fit}.
\end{equation}
A $\chi^2$ corresponding to the agreement between the fitted and measured recoil is reconstructed as (equation \ref{eqn:kinfit_recoilchi2})
~\vspace{-0.5\baselineskip}
\begin{equation}\label{eqn:kinfit_recoilchi2}
\chi^2_{\text{recoil}} = (\vec{p_{\text{T,recoil}}}^{\text{fit}} - \vec{p_{\text{T,recoil}}}^{\text{measured}})^T V_{\text{recoil}}^{-1}(\vec{p_{\text{T,recoil}}}^{\text{fit}} - \vec{p_{\text{T,recoil}}}^{\text{measured}})
\end{equation}
where the covariance matrix $V_{\text{recoil}}$ of the recoil vector is estimated as in equation \ref{eqn:kinfit_recoilcov} from the covariance matrices of the b-jets and
the covariance matrix of the missing transverse momentum. The latter is estimated in the process of determining the MVA \MET as discussed in the
OBJECTS section,
while the covariance matrices of the b-jets can be written in terms of the position, momentum and resolution of the b-jets. 
~\vspace{-0.5\baselineskip}
\begin{equation}\label{eqn:kinfit_recoilcov}
V_{\text{recoil}} = V_{\vec{p_{\text{T,miss}}}} - V_{b_{1}} - V_{b_2} 
\end{equation}
The total $\chi^2$ term that needs to be minimised in the fit can then be written as
~\vspace{-0.5\baselineskip}
\begin{equation}\label{eqn:kinfit_chitot}
\chi^2 = \chi^2_{b_1} + \chi^2_{b_2} + \chi^2_{\text{recoil}}.
\end{equation}
The results of the kinematic fit are the tau and b-jet 4-vectors with their energies and momenta
set to the best fit values found for them in the fit. These can then be added together to find
the mass of the heavy Higgs boson as reconstructed by the kinematic fit.
